---
title: "Breast Cancer Wisconsin (Diagnostic) Data Set"
output: github_document
knit: (function(input, ...) { rmarkdown::render(input, output_file = "README.md", envir = globalenv()) })
---

[Kaggle Link](https://www.kaggle.com/datasets/uciml/breast-cancer-wisconsin-data)

# **IN PROGRESS**

```{r include = F}
knitr::knit_hooks$set(source = function(x, options) {
    hook.r = function(x, options) {
      fence = "```"
      language = tolower(options$engine)
      if (language == "node") language = "javascript"
      if (!options$highlight) language = "text"
      if (!is.null(options$fold_code)) {
        paste0("\n\n", "<details><summary>View Code</summary>\n", fence, language,
               "\n", x, fence, "\n\n", "</details>\n")
      } else paste0('\n\n', fence, language, '\n', x, fence,  '\n\n')
    }
    x = knitr:::hilight_source(x, "markdown", options)
    hook.r(paste(c(x, ""), collapse = "\n"), options)
})
```

___

### Contents

- [Setup]
- [Data Import]
- [Checking for Missing Data]
- [Exploratory Data Analysis]
- [Modeling]

### Setup

```{r message = F, warning = F}
tictoc::tic()

library(tidyverse)
library(tidymodels)
library(tvthemes)
library(janitor)
library(patchwork)
library(ggcorrplot)

theme_custom = theme_avatar() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5, size = 9, vjust = 2.5, face = "italic"),
        panel.grid.major = element_line(linewidth = 0.5, colour = "#D6D0C4"),
        panel.grid.minor = element_line(linewidth = 0.5, colour = "#D6D0C4"))

theme_set(theme_custom)
custom_fills = scale_fill_manual(values = c("springgreen4", "indianred3"))
```

### Data Import

```{r fold_code = T}
df = clean_names(read_csv("breast_cancer_data.csv", col_types = cols()))
paste0("Data Dimensions: ", nrow(df), " Rows, ", ncol(df), " Columns")
```

### Checking for Missing Data

```{r fold_code = T}
colSums(is.na(df))
```

None :)

### Exploratory Data Analysis

___

### Overview of *diagnosis*

```{r fold_code = T}
# renaming `diagnosis` labels
df2 = df |>
  mutate(diagnosis = ifelse(diagnosis == "M", "Malignant", "Benign"))

df2 |>
  count(diagnosis) |>
  ggplot(aes(diagnosis, n)) +
  geom_col(aes(fill = diagnosis), show.legend = F) +
  geom_text(aes(label = n), size = 3.5, vjust = -0.5) +
  scale_fill_manual(values = c("springgreen4", "indianred3")) +
  labs(x = "Diagnosis", y = "Count", title = "Diagnosis Counts") +
  theme(axis.text.y = element_blank())
```

### Overview of *radius_mean*

```{r fold_code = T}
sub_5num = function(x) {
  sub = fivenum(x)
  paste0("Min: ", sub[1], " | Q1: ", sub[2], " | Median: ", sub[3], " | Q3: ", sub[4], " | Max: ", sub[5])
}

df2 |>
  ggplot(aes(radius_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Radius Mean", y = "Density",
       title = "Distribution of Radius Mean by Diagnosis", fill = NULL,
       subtitle = sub_5num(df2$radius_mean))
```

### Overview of *texture_mean*

```{r fold_code = T}
df2 |>
  ggplot(aes(texture_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Texture Mean", y = "Density",
       title = "Distribution of Texture Mean by Diagnosis", fill = "Diagnosis",
       subtitle = sub_5num(df2$texture_mean))
```

### Overview of *perimeter_mean*

```{r fold_code = T}
df2 |>
  ggplot(aes(perimeter_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Perimeter Mean", y = "Density", fill = "Diagnosis",
       title = "Distribution of Perimeter Mean by Diagnosis",
       subtitle = sub_5num(df2$perimeter_mean))
```

### Overview of *area_mean*

```{r fold_code = T}
df2 |>
  ggplot(aes(area_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Area Mean", y = "Density", fill = "Diagnosis",
       title = "Distribution of Area Mean by Diagnosis",
       subtitle = sub_5num(df2$area_mean))
```

### Overview of *smoothness_mean*

```{r fold_code = T}
df2 |>
  ggplot(aes(smoothness_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Smoothness Mean", y = "Density", fill = "Diagnosis",
       title = "Distribution of Smoothness Mean by Diagnosis",
       subtitle = sub_5num(df2$smoothness_mean))
```

### Overview of *compactness_mean*

```{r fold_code = T}
df2 |>
  ggplot(aes(compactness_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Compactness Mean", y = "Density", fill = "Diagnosis",
       title = "Distribution of Compactness Mean by Diagnosis",
       subtitle = sub_5num(df2$compactness_mean))
```

### Overview of *concavity_mean*

```{r fold_code = T}
df2 |>
  ggplot(aes(concavity_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Concavity Mean", y = "Density", fill = "Diagnosis",
       title = "Distribution of Concavity Mean by Diagnosis",
       subtitle = sub_5num(df2$concavity_mean))
```

### Overview of *concave_points_mean*

```{r fold_code = T}
df2 |>
  ggplot(aes(concave_points_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Concave Points Mean", y = "Density", fill = "Diagnosis",
       title = "Distribution of Concave Points Mean by Diagnosis",
       subtitle = sub_5num(df2$concave_points_mean))
```

### Overview of *symmetry_mean*

```{r fold_code = T}
df2 |>
  ggplot(aes(symmetry_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Symmetry Mean", y = "Density", fill = "Diagnosis",
       title = "Distribution of Symmetry Mean by Diagnosis",
       subtitle = sub_5num(df2$symmetry_mean))
```

### Overview of *fractal_dimension_mean*

```{r fold_code = T}
df2 |>
  ggplot(aes(fractal_dimension_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Fractal Dimension Mean", y = "Density", fill = "Diagnosis",
       title = "Distribution of Fractal Dimension Mean by Diagnosis",
       subtitle = sub_5num(df2$fractal_dimension_mean))
```

### Overview of *radius_se*

```{r fold_code = T}
df2 |>
  ggplot(aes(radius_se)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Radius Standard Error", y = "Density", fill = "Diagnosis",
       title = "Distribution of Radius Standard Error by Diagnosis",
       subtitle = sub_5num(df2$radius_se))
```

### Overview of *texture_se*

```{r fold_code = T}
df2 |>
  ggplot(aes(texture_se)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Texture Standard Error", y = "Density", fill = "Diagnosis",
       title = "Distribution of Texture Standard Error by Diagnosis",
       subtitle = sub_5num(df2$texture_se))
```

### Overview of *perimeter_se*

```{r fold_code = T}
df2 |>
  ggplot(aes(perimeter_se)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Perimeter Standard Error", y = "Density", fill = "Diagnosis",
       title = "Distribution of Perimeter Standard Error by Diagnosis",
       subtitle = sub_5num(df2$perimeter_se))
```

### Overview of *area_se*

```{r fold_code = T}
df2 |>
  ggplot(aes(area_se)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Area Standard Error", y = "Density", fill = "Diagnosis",
       title = "Distribution of Area Standard Error by Diagnosis",
       subtitle = sub_5num(df2$area_se))
```

### Overview of *smoothness_se*

```{r fold_code = T}
df2 |>
  ggplot(aes(smoothness_se)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Smoothness Standard Error", y = "Density", fill = "Diagnosis",
       title = "Distribution of Smoothness Standard Error by Diagnosis",
       subtitle = sub_5num(df2$smoothness_se))
```

### Overview of *compactness_se*

```{r fold_code = T}
df2 |>
  ggplot(aes(compactness_se)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Compactness Standard Error", y = "Density", fill = "Diagnosis",
       title = "Distribution of Compactness Standard Error by Diagnosis",
       subtitle = sub_5num(df2$compactness_se))
```

### Overview of *concavity_se*

```{r fold_code = T}
df2 |>
  ggplot(aes(concavity_se)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Concavity Standard Error", y = "Density", fill = "Diagnosis",
       title = "Distribution of Concavity Standard Error by Diagnosis",
       subtitle = sub_5num(df2$concavity_se))
```

### Overview of *concave_points_se*

```{r fold_code = T}
df2 |>
  ggplot(aes(concave_points_se)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Concave Points Standard Error", y = "Density", fill = "Diagnosis",
       title = "Distribution of Concave Points Standard Error by Diagnosis",
       subtitle = sub_5num(df2$concave_points_se))
```

### Overview of *symmetry_se*

```{r fold_code = T}
df2 |>
  ggplot(aes(symmetry_se)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Symmetry Standard Error", y = "Density", fill = "Diagnosis",
       title = "Distribution of Symmetry Standard Error by Diagnosis",
       subtitle = sub_5num(df2$symmetry_se))
```

### Overview of *fractal_dimension_se*

```{r fold_code = T}
df2 |>
  ggplot(aes(fractal_dimension_se)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Fractal Dimension Standard Error", y = "Density", fill = "Diagnosis",
       title = "Distribution of Fractal Dimension Standard Error by Diagnosis",
       subtitle = sub_5num(df2$fractal_dimension_se))
```

### Overview of *radius_worst*

```{r fold_code = T}
df2 |>
  ggplot(aes(radius_worst)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Radius Worst", y = "Density", fill = "Diagnosis",
       title = "Distribution of Radius Worst by Diagnosis",
       subtitle = sub_5num(df2$radius_worst))
```

### Overview of *texture_worst*

```{r fold_code = T}
df2 |>
  ggplot(aes(texture_worst)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Texture Worst", y = "Density", fill = "Diagnosis",
       title = "Distribution of Texture Worst by Diagnosis",
       subtitle = sub_5num(df2$texture_worst))
```

### Overview of *perimeter_worst*

```{r fold_code = T}
df2 |>
  ggplot(aes(perimeter_worst)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Perimeter Worst", y = "Density", fill = "Diagnosis",
       title = "Distribution of Perimeter Worst by Diagnosis",
       subtitle = sub_5num(df2$perimeter_worst))
```

### Overview of *area_worst*

```{r fold_code = T}
df2 |>
  ggplot(aes(area_worst)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Area Worst", y = "Density", fill = "Diagnosis",
       title = "Distribution of Area Worst by Diagnosis",
       subtitle = sub_5num(df2$area_worst))
```

### Overview of *smoothness_worst*

```{r fold_code = T}
df2 |>
  ggplot(aes(smoothness_worst)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Smoothness Worst", y = "Density", fill = "Diagnosis",
       title = "Distribution of Smoothness Worst by Diagnosis",
       subtitle = sub_5num(df2$smoothness_worst))
```

### Overview of *compactness_worst*

```{r fold_code = T}
df2 |>
  ggplot(aes(compactness_worst)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Compactness Worst", y = "Density", fill = "Diagnosis",
       title = "Distribution of Compactness Worst by Diagnosis",
       subtitle = sub_5num(df2$compactness_worst))
```

### Overview of *concavity_worst*

```{r fold_code = T}
df2 |>
  ggplot(aes(concavity_worst)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Concavity Worst", y = "Density", fill = "Diagnosis",
       title = "Distribution of Concavity Worst by Diagnosis",
       subtitle = sub_5num(df2$concavity_worst))
```

### Overview of *concave_points_worst*

```{r fold_code = T}
df2 |>
  ggplot(aes(concave_points_worst)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Concave Points Worst", y = "Density", fill = "Diagnosis",
       title = "Distribution of Concave Points Worst by Diagnosis",
       subtitle = sub_5num(df2$concave_points_worst))
```

### Overview of *symmetry_worst*

```{r fold_code = T}
df2 |>
  ggplot(aes(symmetry_worst)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Symmetry Worst", y = "Density", fill = "Diagnosis",
       title = "Distribution of Symmetry Worst by Diagnosis",
       subtitle = sub_5num(df2$symmetry_worst))
```

### Overview of *fractal_dimension_worst*

```{r fold_code = T}
df2 |>
  ggplot(aes(fractal_dimension_worst)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Fractal Dimension Worst", y = "Density", fill = "Diagnosis",
       title = "Distribution of Fractal Dimension Worst by Diagnosis",
       subtitle = sub_5num(df2$fractal_dimension_worst))
```

### Correlation Plot for All *mean* Variables

```{r fold_code = T}
df2 |>
  select(contains("mean")) |>
  cor() |>
  ggcorrplot(lab = T, type = "lower", lab_size = 3,
             colors = c("indianred3", "white", "springgreen4"))
```

### Correlation Plot for All *se* Variables

```{r fold_code = T}
df2 |>
  select(contains("se")) |>
  cor() |>
  ggcorrplot(lab = T, type = "lower", lab_size = 3,
             colors = c("indianred3", "white", "springgreen4"))
```

### Correlation Plot for All *worst* Variables

```{r fold_code = T}
df2 |>
  select(contains("worst")) |>
  cor() |>
  ggcorrplot(lab = T, type = "lower", lab_size = 3,
             colors = c("indianred3", "white", "springgreen4"))
```

This will conclude the exploratory portion of the analysis, and I will now move onto the modeling portion.

### Modeling

___

### Data Splitting

```{r fold_code = T}
data_split = initial_split(df2, prop = 0.8, strata = diagnosis)
train_data = training(data_split)
test_data = testing(data_split)
paste0("Training Data: ", nrow(train_data), " Observations; Testing Data: ", nrow(test_data), " Observations")
```

### Examining Distribution of *diagnosis* Across Data Splits

```{r fold_code = T}
train_data |>
  count(diagnosis) |>
  mutate(set = "Training Data",
         pct = round(n / sum(n), 3),
         pct_lab = paste0(pct * 100, "%")) |>
  bind_rows(test_data |>
              count(diagnosis) |>
              mutate(set = "Testing Data",
                     pct = round(n / sum(n), 3),
                     pct_lab = paste0(pct * 100, "%"))) |>
  mutate(set = factor(set, levels = c("Training Data", "Testing Data"))) |>
  ggplot(aes(set, pct)) +
  geom_col(aes(fill = diagnosis), position = "dodge") +
  geom_text(aes(label = pct_lab), position = position_dodge2(width = 1), vjust = -0.5, size = 3.5) +
  coord_cartesian(ylim = c(0, 0.65)) +
  scale_fill_manual(values = c("springgreen4", "indianred3")) +
  labs(x = "Dataset", y = "Percent of Observations", fill = NULL,
       title = "Proportional Diagnoses Across Training and Testing Data") +
  theme(legend.position = "right")
```

### Data Preprocessing

```{r fold_code = T}
pre_rec = recipe(diagnosis ~ ., data = df2) |>
  update_role(id, new_role = "ID") |>
  # normalizes predictors
  step_normalize(all_predictors()) |>
  # removes predictors with zero variance
  step_zv(all_predictors()) |>
  # removes highly-correlated predictors, we can control the threshold at which they are removed
  step_corr(all_predictors(), threshold = 0.8, method = "spearman")

pre_rec
```

### Previewing Preprocessed Data

```{r fold_code = T}
pre_rec |>
  prep() |>
  juice() |>
  sample_n(10)
```

### Building Cross Validation Folds

```{r fold_code = T}
cv_folds = vfold_cv(train_data, v = 5, strata = diagnosis)
cv_folds
```

### Building Logistic Regression Specification and Workflow

```{r fold_code = T}
log_spec = logistic_reg() |>
  set_engine("glm") |>
  set_mode("classification")

log_wflow = workflow() |>
  add_recipe(pre_rec) |>
  add_model(log_spec)

log_wflow
```

### Getting Logistic Regression Results

```{r message = F, warning = F, fold_code = T}
log_res = log_wflow |>
  fit_resamples(resamples = cv_folds,
                metrics = metric_set(accuracy, f_meas, roc_auc),
                control = control_resamples(save_pred = T))

log_res |>
  collect_metrics() |>
  select(.metric, mean, std_err)
```

### Building Random Forest Specification and Workflow

```{r fold_code = T}
rf_spec = rand_forest() |>
  set_engine("ranger", importance = "impurity") |>
  set_mode("classification")

rf_wflow = workflow() |>
  add_recipe(pre_rec) |>
  add_model(rf_spec)

rf_wflow
```

### Getting Random Forest Results

```{r message = F, warning = F, fold_code = T}
rf_res = rf_wflow |>
  fit_resamples(resamples = cv_folds,
                metrics = metric_set(accuracy, f_meas, roc_auc),
                control = control_resamples(save_pred = T))

rf_res |>
  collect_metrics() |>
  select(.metric, mean, std_err)
```

### Building XGBoost Specification and Workflow

```{r fold_code = T}
xgb_spec = boost_tree() |>
  set_engine("xgboost") |>
  set_mode("classification")

xgb_wflow = workflow() |>
  add_recipe(pre_rec) |>
  add_model(xgb_spec)

xgb_wflow
```

### Getting XGBoost Results

```{r message = F, warning = F, fold_code = T}
xgb_res = xgb_wflow |>
  fit_resamples(resamples = cv_folds,
                metrics = metric_set(accuracy, f_meas, roc_auc),
                control = control_resamples(save_pred = T))

xgb_res |>
  collect_metrics() |>
  select(.metric, mean, std_err)
```

### Comparing Model Results

```{r fold_code = T}
three_mod_res = log_res |>
  collect_metrics() |>
  select(.metric, mean, std_err) |>
  mutate(model = "Logistic Regression") |>
  bind_rows(rf_res |>
              collect_metrics() |>
              select(.metric, mean, std_err) |>
              mutate(model = "Random Forest")) |>
  bind_rows(xgb_res |>
              collect_metrics() |>
              select(.metric, mean, std_err) |>
              mutate(model = "XGBoost"))

lr_res = three_mod_res |>
  filter(model == "Logistic Regression") |>
  mutate(mean = paste0(round(mean, 4) * 100, "%"))

lr_acc = lr_res$mean[1]
lr_f1 = lr_res$mean[2]
lr_roc = lr_res$mean[3]

three_mod_res |>
  ggplot(aes(.metric, mean)) +
  geom_col(aes(fill = model), position = "dodge") +
  geom_text(aes(label = round(mean, 4)), size = 3.5, position = position_dodge2(width = 0.9), vjust = -0.5) +
  coord_cartesian(ylim = c(0.9, 1)) +
  labs(x = "Evaluation Metric", y = "Value", fill = NULL,
       title = "Evaluation Metrics Across Models")
```

After this initial modeling step, we have achieved an accuracy of `r lr_acc`, an F1 score of `r lr_f1`, and an AUC value of `r lr_roc` with a logistic regression model. We have achieved similar results with our random forest and XGBoost models as well, and will now tune the hyperparameters for those models to see if we can improve upon our current results.

### Random Forest Tuning

```{r fold_code = T}
tune_spec = rand_forest(trees = 1000, mtry = tune(), min_n = tune()) |>
  set_mode("classification") |>
  set_engine("ranger")

tune_wf = workflow() |>
  add_recipe(pre_rec) |>
  add_model(tune_spec)

doParallel::registerDoParallel()
tune_res = tune_grid(tune_wf, resamples = cv_folds, grid = 25)

tune_res |>
  show_best("accuracy")
```

### XGBoost Tuning

```{r fold_code = T}
xgb_spec = boost_tree(trees = 1000, tree_depth = tune(), min_n = tune(),
                      loss_reduction = tune(), sample_size = tune(),
                      mtry = tune(), learn_rate = tune()) |>
  set_engine("xgboost") |>
  set_mode("classification")

xgb_grid = grid_latin_hypercube(tree_depth(), min_n(), loss_reduction(),
                                sample_size = sample_prop(), finalize(mtry(), train_data),
                                learn_rate(), size = 30)

xgb_wf = workflow() |>
  add_recipe(pre_rec) |>
  add_model(xgb_spec)

doParallel::registerDoParallel()
xgb_res = tune_grid(xgb_wf, resamples = cv_folds, grid = xgb_grid, control = control_grid(save_pred = T))

xgb_res |>
  show_best("roc_auc")
```

### Post-Tuning Model Comparison

```{r fold_code = T}
lr_acc = collect_metrics(log_res) |>
  filter(.metric == "accuracy") |>
  pull(mean) |>
  round(4)

lr_auc = collect_metrics(log_res) |>
  filter(.metric == "roc_auc") |>
  pull(mean) |>
  round(4)

rf_acc = show_best(tune_res, metric = "accuracy", n = 1) |>
  pull(mean) |>
  round(4)

rf_auc = show_best(tune_res, metric = "roc_auc", n = 1) |>
  pull(mean) |>
  round(4)

xgb_acc = show_best(xgb_res, metric = "accuracy", n = 1) |>
  pull(mean) |>
  round(4)

xgb_auc = show_best(xgb_res, metric = "roc_auc", n = 1) |>
  pull(mean) |>
  round(4)

data.frame(model = c("Logistic Regression", "Random Forest", "XGBoost"),
           accuracy = c(lr_acc, rf_acc, xgb_acc),
           roc_auc = c(lr_auc, rf_auc, xgb_auc)) |>
  pivot_longer(!model, names_to = "metric", values_to = "value") |>
  ggplot(aes(metric, value)) +
  geom_col(aes(fill = model), position = "dodge") +
  geom_text(aes(label = value), position = position_dodge2(width = 0.9), vjust = -0.5, size = 3.5) +
  labs(title = "Post-Tuning Model Comparison", fill = NULL, x = "Evaluation Metric", y = "Value")
```

















### Script Runtime

```{r}
tictoc::toc()
```

































