---
title: "Breast Cancer Wisconsin (Diagnostic) Data Set"
output: github_document
knit: (function(input, ...) { rmarkdown::render(input, output_file = "README.md", envir = globalenv()) })
---

# **IN PROGRESS**

```{r include = F}
knitr::knit_hooks$set(source = function(x, options) {
    hook.r = function(x, options) {
      fence = "```"
      language = tolower(options$engine)
      if (language == "node") language = "javascript"
      if (!options$highlight) language = "text"
      if (!is.null(options$fold_code)) {
        paste0("\n\n", "<details><summary>View Code</summary>\n", fence, language,
               "\n", x, fence, "\n\n", "</details>\n")
      } else paste0('\n\n', fence, language, '\n', x, fence,  '\n\n')
    }
    x = knitr:::hilight_source(x, "markdown", options)
    hook.r(paste(c(x, ""), collapse = "\n"), options)
})
```

___

### Setup

```{r message = F, warning = F}
library(tidyverse)
library(tidymodels)
library(tvthemes)
library(janitor)
library(patchwork)

theme_custom = theme_avatar() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5, size = 9, vjust = 2.5, face = "italic"),
        panel.grid.major = element_line(linewidth = 0.5, colour = "#D6D0C4"),
        panel.grid.minor = element_line(linewidth = 0.5, colour = "#D6D0C4"))

theme_set(theme_custom)
custom_fills = scale_fill_manual(values = c("springgreen4", "indianred3"))
```

### Data Import

```{r fold_code = T}
df = clean_names(read_csv("breast_cancer_data.csv", col_types = cols()))
paste0("Data Dimensions: ", nrow(df), " Rows, ", ncol(df), " Columns")
```

### Checking for Missing Data

```{r fold_code = T}
colSums(is.na(df))
```

None :)

### Overview of *diagnosis*

```{r fold_code = T}
# renaming `diagnosis` labels
df2 = df |>
  mutate(diagnosis = ifelse(diagnosis == "M", "Malignant", "Benign"))

df2 |>
  count(diagnosis) |>
  ggplot(aes(diagnosis, n)) +
  geom_col(aes(fill = diagnosis), show.legend = F) +
  geom_text(aes(label = n), size = 3.5, vjust = -0.5) +
  scale_fill_manual(values = c("springgreen4", "indianred3")) +
  labs(x = "Diagnosis", y = "Count", title = "Diagnosis Counts") +
  theme(axis.text.y = element_blank())
```

### Overview of *radius_mean*

```{r fold_code = T}
sub_5num = function(x) {
  sub = fivenum(x)
  paste0("Min: ", sub[1], " | Q1: ", sub[2], " | Median: ", sub[3], " | Q3: ", sub[4], " | Max: ", sub[5])
}

df2 |>
  ggplot(aes(radius_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Radius Mean", y = "Density",
       title = "Distribution of Radius Mean by Diagnosis", fill = NULL,
       subtitle = sub_5num(df2$radius_mean))
```

### Overview of *texture_mean*

```{r fold_code = T}
df2 |>
  ggplot(aes(texture_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Texture Mean", y = "Density",
       title = "Distribution of Texture Mean by Diagnosis", fill = "Diagnosis",
       subtitle = sub_5num(df2$texture_mean))
```

### Overview of *perimeter_mean*

```{r fold_code = T}
df2 |>
  ggplot(aes(perimeter_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Perimeter Mean", y = "Density", fill = "Diagnosis",
       title = "Distribution of Perimeter Mean by Diagnosis",
       subtitle = sub_5num(df2$perimeter_mean))
```

### Overview of *area_mean*

```{r fold_code = T}
df2 |>
  ggplot(aes(area_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Area Mean", y = "Density", fill = "Diagnosis",
       title = "Distribution of Area Mean by Diagnosis",
       subtitle = sub_5num(df2$area_mean))
```

### Overview of *smoothness_mean*

```{r fold_code = T}
df2 |>
  ggplot(aes(smoothness_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Smoothness Mean", y = "Density", fill = "Diagnosis",
       title = "Distribution of Smoothness Mean by Diagnosis",
       subtitle = sub_5num(df2$smoothness_mean))
```

### Overview of *compactness_mean*

```{r fold_code = T}
df2 |>
  ggplot(aes(compactness_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Compactness Mean", y = "Density", fill = "Diagnosis",
       title = "Distribution of Compactness Mean by Diagnosis",
       subtitle = sub_5num(df2$compactness_mean))
```

### Overview of *concavity_mean*

```{r fold_code = T}
df2 |>
  ggplot(aes(concavity_mean)) +
  geom_density(aes(fill = diagnosis), alpha = 0.5, col = "transparent") +
  custom_fills +
  labs(x = "Concavity Mean", y = "Density", fill = "Diagnosis",
       title = "Distribution of Concavity Mean by Diagnosis",
       subtitle = sub_5num(df2$concavity_mean))
```

























































